Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law

### 2023-12-07 manuscript/manuscript.qmd
Remove second RO definition

The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China. The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations (ROs), or (2) filing documentation of temporary activities with provincial Public Security Bureaus. Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year. Using one of these two channels to obtain legal status became mandatory in 2017. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.

>>>>

The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China. The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations, or (2) filing documentation of temporary activities with provincial Public Security Bureaus. Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year. Using one of these two channels to obtain legal status became mandatory in 2017. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.
